### 2019-03-07 manuscript/methods.tex

The effects of breeding system in the diversification process were modeled using the self-incompatible (I) or self-compatible (C) states on the tips of the phylogeny.
The proposed model is similar to the  analysis proposed by  \citet{goldberg_2010} but applied to the much larger dataset.
The proposed model is also BiSSE-like and we refer to it as the \textit{I/C breeding system} model. 
In order to parse out the effect of breeding system on diversification, while allowing for the possibility of heterogeneous diversification rates unrelated to breeding system, we subdivided each of those states into hidden states $A$ and $B$.
We call this HiSSE model the \textit{I/C+A/B breeding system and hidden state model} . The I/C+A/B model is equivalent to the model used in \citet{freyman_2017} but we restricted the hidden state transition rates to be symmetrical.

@@

For all four models that consider ploidy changes, we allowed diploidization by adding a parameter $\delta$ connecting polyploidy state back to diploid or to self-compatible diploid in the mult-state models (denoted by $+/delta$ in the models of  \cref{table:marginallike}).
Previous modeling approaches \citep{mayrose_2011} have argued against inferring diploidization rates when using ploidy data that comes from classifications based on chromosome number multiplicity or chromosome number change models like chromEvol \citep{mayrose_2010, mayrose_2015}.
These types of classifications do not allow for a ploidy reversion.
Where indicated, the classification of ploidy for the data used in our models was based on chromosome multiplicity at the genus level (data available at https://www.github.com/roszenil/solploidy/datasets).
% ref data/sources table?
%github
However, the majority of the ploidy classifications were adopted from original studies with alternative sources of information (\eg geographic distribution, genus ploidy distribution) where ploidy was defined by authors that found evidence for it.
Since it is not clear whether diploidization can be detected under alternative ploidy classifications or even classifications based on chromosome number multiplicity at the genus level, we also fit the models without diploidization in order to test  whether the conclusions about diversification are sensitive to including diploidization.
As discussed by \citet{servedio_2014}, the presence or absence of a hypothesis can have an exploratory goal.
In our case the diploidization parameter (or its absence, $\delta=0$) in our models is an opportunity to explore an assumption that might be important but that is not the single definitive process to understand the interactions among polyploidy, breeding system, and diversification.

>>>>

To assess the effects of breeding system in the diversification process, we first fit model in which the states are self-incompatible (I) or self-compatible (C).
This is the same as the analysis of \citet{goldberg_2010}, but with an updated phylogeny \citep{sarkinen_2013}.
We call this BiSSE model the \textit{I/C breeding system} model. 
To parse out the effect of breeding system on diversification, while allowing for the possibility of heterogeneous diversification rates unrelated to breeding system, we subdivided each of those states into hidden states $A$ and $B$.
We call this HiSSE model the \textit{I/C+A/B breeding system and hidden state model}.
The I/C+A/B model is equivalent to the model \citet{freyman_2017} used to study diversification in Onagraceae, but we restricted the hidden state transition rates to be symmetrical.

@@

For all four models that consider ploidy changes, we allowed diploidization by adding a parameter $\delta$ connecting polyploidy state back to diploid or to self-compatible diploid in the mult-state models (denoted by $+/delta$ in the models of  \cref{table:marginallike}).
Previous modeling approaches \citep{mayrose_2011} have argued against inferring diploidization rates when using ploidy data that comes from classifications based on chromosome number multiplicity or chromosome number change models like chromEvol \citep{mayrose_2010, glick2014, mayrose_2015, freyman_2017}.
These types of classifications do not allow for a ploidy reversion.
Where indicated, the classification of ploidy for the data used in our models was based on chromosome multiplicity at the genus level (data available at https://www.github.com/roszenil/solploidy/datasets).
% ref data/sources table?
%github
However, the majority of the ploidy classifications were adopted from original studies with alternative sources of information (\eg geographic distribution, genus ploidy distribution) where ploidy was defined by authors that found evidence for it.
Since it is not clear whether diploidization can be detected under alternative ploidy classifications or even classifications based on chromosome number multiplicity at the genus level, we also fit the models without diploidization in order to test  whether the conclusions about diversification are sensitive to including diploidization.
As discussed by \citet{servedio_2014}, the presence or absence of a hypothesis can have an exploratory goal.
In our case the diploidization parameter (or its absence, $\delta=0$) in our models is an opportunity to explore an assumption that might be important but that is not the single definitive process to understand the interactions among polyploidy, breeding system, and diversification.
